Composition-climate paper

### 2015-07-24 Composition_Ecology.Rmd
Added some comments based on discussion with @andydawson 24/7/2015.

@@

The choice of a normal for the domain is potentially problematic.  The time transgressive nature of the PLS Survey means that some of the PLS data comes from records sampled in the early 1800s, while other come from the early 1900s. Regardless, throughout this period climate variability exists (Figure 1e), and trees that were on the landscape from the 1830s to the 1880s are not expected to have been completely extirpated by annual scale climate variability in that same time period. As such the use of a 'pre-settlement' climate normal from 1895-1925 is likely a reasonable choice [ADD JULY temperatures here].

>>>>

**Paragraph about data scale between PLS and FIA**

**Paragraph about FIA/PLS absence not really Absence**

@@

The choice of a normal for the domain is potentially problematic.  The time transgressive nature of the PLS Survey means that some of the PLS data comes from records sampled in the early 1800s, while other come from the early 1900s. Regardless, throughout this period climate variability exists (Figure 1d), and trees that were on the landscape from the 1830s to the 1880s are not expected to have been completely extirpated by annual scale climate variability in that same time period. As such the use of a 'pre-settlement' climate normal from 1895-1925 is likely a reasonable choice [ADD JULY temperatures here]. **Talk about modern climate normal & historical climate normal make it clear that this is the best we can do, and that it's good.**
